%% -*- LaTeX -*-
\documentclass{report}

\usepackage{thesis}

%some other packages I found useful, comment out or remove if you do not need them
\usepackage{amsmath}
\usepackage{url}
\usepackage{subfigure}
\usepackage[pdftex]{graphicx}
\usepackage{multirow}
\usepackage{chapterbib}
\usepackage{amssymb}
\usepackage[titletoc,toc,title]{appendix}
\usepackage{titlesec}

\usepackage{cite}
\usepackage{tabularx}

\widowpenalty=1000000
\clubpenalty=1000000


\title{A Concrete Work of Abstract Genius}
\author{John Doe}
\defensedate{February 26, 2013}
\dissertation                             %% or \dissertation
\doctorphilosophy                      %% or \doctorphilosophy or \masterarts
\cs                                 %% this is the only speciality defined.
\maygrad                            %% or \octgrad or \marchgrad
\advisor{Bunny Lebowski, Ph.D.}
\readerone{Walter Sobchak, Ph.D.}
\readertwo{Carl Hungus, Ph.D.}      %% Optional if MS.
\chair{V.I. Lenin, Ph.D.}



\begin{document}
\maketitle
\makeacceptance

\begin{abstract}
This a concrete work of abstract genius, comparable only to G\"odel's second
incompleteness result, and John Fante's ``1933 Was A Bad Year.''
\end{abstract}

\begin{citationspage}
\citationheadingpublished
\noindent Doe, J. and B. Lebowski. (2009). My First Published Paper. {\it Proceedings of the IEEE Congress on Life}.
\\ \\
\noindent Doe, J. and B. Lebowski. (2010). My Second Published Paper. {\it The World's Greatest Journal}.

%if have unpublished work, use one or more of the following
\begin{center}
\vskip 2em
{\large AND}
\end{center}
\vskip 2em 
Material from this dissertation has been accepted for publication in {\it Fantastic Journal} on 05/20/2013 in the following form:\\
\vskip 2em 
\noindent Doe, J. and B. Lebowski. (2013). Soon To Be Published Paper. {\it Fantastic Journal}.

\begin{center}
\vskip 2em
{\large AND}
\end{center}
\vskip 2em 
Material from this dissertation has been submitted for publication in {\it Some Other Journal} on 04/30/2013 in the following form:\\
\vskip 2em 
\noindent Doe, J. and B. Lebowski. (2013). Paper In Review. {\it Some Other Journal}.

\end{citationspage}

\begin{dedication} %% Optional
{\large 
{\it in memory of} 
\\
\vskip 2em
Alan Turing (1912-1954)}
\end{dedication}

\begin{acknowledgements}  %% Optional
I'd like to take this opportunity to pour a little of my 40oz. out for all
the homies that didn't make it.
\end{acknowledgements}

\tableofcontents
\listoffigures
\listoftables

\mainmatter
\sloppy

%for journal format dissertation each chapter needs its own reference section, and want references to be included in global bibliography
%this is accomplished using include commands
%but, for things like the lit review (chapter 1) or an appendix, should use input so it does not get it's own references section

%if not doing a journal format dissertation you can just use input for all chapters, or put text here directly.
\input{chapter1}
\include{chapter2}
\include{chapter3}

\bibliographystyle{chicago}
\bibliography{example}

\input{appendix}

\end{document}
